The Noisy Work of Uncertainty Visualisation Research: A Review

### 2024-09-24 paper.qmd
changed underlying spatial trend

my_map_data <- my_map_data |>
  dplyr::mutate(temp = 28 - ((scale(cent_long))^(2) + (scale(cent_lat))^(2))[,1], # trend
         notrend = rnorm(n), # no trend
         highvar = runif(n, min=1, max=2), # high variance
         lowvar = runif(n, min=0, max=1), # low variance
         ) |>
  mutate(highvar = highvar^2,
         lowvar = lowvar^2,
         count_id = row_number()) |>
  pivot_longer(cols=highvar:lowvar, names_to = "variance_class", values_to = "variance") |>
  # add bivariate classes to data
  mutate(bitemp = cut(temp, breaks=breaks, labels=seq(8)),
         bivar = cut(variance, breaks=0:4, labels=seq(4)),
         biclass = paste(bitemp, bivar, sep="-"))

@@

# make blank map 
example_map <- my_map_data |>
  filter(variance_class=="lowvar") |>
  ggplot() +
  geom_sf(aes(geometry = geometry), fill="white") + 
  #geom_text(aes(x=cent_long, y=cent_lat, label=count_id), size=2) +
  theme_void()

@@

p1a
p1b

show_pal(basecols, ncol=8, borders=NA, myxlab = "Temperature", breaks = 21:29, textnudge = c(0.2, 0.1, 0,0,0,0,0,-0.1,-0.2), xlabx= 4, xlaby=-1.75)

>>>>

my_map_data <- my_map_data |>
  dplyr::mutate(temp = 29 - 3*abs(scale(cent_lat) - sin(2*(scale(cent_long)))[,1]), # trend
         notrend = rnorm(n), # no trend
         highvar = runif(n, min=1, max=2), # high variance
         lowvar = runif(n, min=0, max=1), # low variance
         ) |>
  mutate(highvar = highvar^2,
         lowvar = lowvar^2,
         count_id = row_number()) |>
  pivot_longer(cols=highvar:lowvar, names_to = "variance_class", values_to = "variance") |>
  # add bivariate classes to data
  mutate(bitemp = cut(temp, breaks=breaks, labels=seq(8)),
         bivar = cut(variance, breaks=0:4, labels=seq(4)),
         biclass = paste(bitemp, bivar, sep="-"))

@@

# make blank map 
example_map <- my_map_data |>
  filter(variance_class=="lowvar") |>
  ggplot() +
  geom_sf(aes(geometry = geometry), fill="white") + 
  geom_text(aes(x=cent_long, y=cent_lat, label=count_id), size=2) +
  theme_void()

@@

p1a
p1b
show_pal(basecols, ncol=8, borders=NA, myxlab = "Temperature", breaks = 21:29, textnudge = c(0.2, 0.1, 0,0,0,0,0,-0.1,-0.2), xlabx= 4, xlaby=-1.75)
